Deeply Virtual Compton Scattering measurement off bound protons

### 2018-08-27 eg6-letters/incoherent/incoherent_prl.tex
minor correction
some cleaning after stepans comments

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework.  To explore this idea, we construct the ratio of $A_{LU}$ for bound 
protons to that on a free proton target. 
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from CLAS \cite{Girod:2007aa} as 
a function of the kinematical variable $x_B$. The $A_{LU}$ ratios show 
20\%-40\% lower asymmetries for a bound proton compared to the free proton 
mirroring the EMC effect but with a surprising large modification, in 
particular at low $x_B$. The measurements disagree with the off-shell 
\cite{simonetta_2} and the on-shell calculations that use the medium modified 
GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. In 
particular, the difference becomes large at lower $x_B$, where the off-shell 
model predicts an enhancement of the ratio, while our experiment shows no sign 
of an increase of ratios. This measurement shows that an important nuclear 
effect is missing from the existing models in order to explain this strong 
quenching of the BSA. More theoretical developments will be needed to identify 
the origin of this quenching, in particular it will be key to differenciate 
initial from final state effects and how they can affect the DVCS assymetries.

\begin{figure}[tb]
\centering
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$ as a function of $t$. The black squares are from this 
   work, the green circle is the HERMES measurement \cite{Airapetian:2009cga}.  
   The error bars represent the statistical uncertainties, while the gray bands 
   represent the systematic uncertainties. The blue and red curves are results 
   of off-shell calculations \cite{simonetta_2}. The solid and dashed black 
   curves are from on-shell calculations \cite{Guzey:2008fe}.} 
   \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

>>>>

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework.  To explore this idea, we construct the ratio of $A_{LU}$ for bound 
protons to that on a free proton target. 
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from CLAS \cite{Girod:2007aa} as a 
function of the kinematical variable $t$. The $A_{LU}$ ratios show 25\%-40\% 
lower asymmetries and independent of $t$ for a bound proton compared to the 
free proton. The measurements disagree with the off-shell \cite{simonetta_2} 
and the on-shell calculations that use the medium modified GPDs as calculated 
from the quark-meson coupling model \cite{Guzey:2008fe}. In particular, the 
difference becomes large at lower $x_B$, where the off-shell model predicts an 
enhancement of the ratio, while our experiment shows no sign of an increase of 
ratios. This measurement shows that an important nuclear effect is missing from 
the existing models in order to explain this strong quenching of the BSA. More 
theoretical developments will be needed to identify the origin of this 
quenching, in particular it will be key to differenciate initial from final 
state effects and how they can affect the DVCS assymetries.

\begin{figure}[tb]
\centering
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$ as a function of $t$. The black squares are from this 
   work, the green circle is the HERMES measurement \cite{Airapetian:2009cga}.  
   The error bars represent the statistical uncertainties, while the gray band 
   represents the systematic uncertainties. The blue and red curves are results 
   of off-shell calculations \cite{simonetta_2}. The solid and dashed black 
   curves are from on-shell calculations \cite{Guzey:2008fe}.} 
   \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}
